### 2020-08-14 code/supplemental_v2.Rmd
Add ST1

---
output:
  bookdown::pdf_book:
    number_sections: FALSE
    toc: FALSE
    keep_tex: yes
always_allow_html: TRUE
editor_options:
  chunk_output_type: console
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=600, warning = FALSE, message = FALSE)
suppressPackageStartupMessages(c(
  library(tidyverse),
  library(data.table),
  library(plot3D),
  library(flextable)
))
```

@@

```{r enrich-pathway-in-clust, eval = FALSE}
## docx friendly
load("../data/moderate_enrich_prob.Rda")

@@

st1 %>% flextable() %>% 
  set_caption(caption = "") %>%
  align(part = "all") %>% 
  width(., width = c(4,0.75,1,1)) %>% 
  fontsize(size = 10, part = "body")
```

>>>>

---
output:
  bookdown::pdf_book:
    number_sections: FALSE
    toc: FALSE
    keep_tex: yes
always_allow_html: TRUE
editor_options:
  chunk_output_type: console
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=600, warning = FALSE, message = FALSE)
suppressPackageStartupMessages(c(
  library(tidyverse),
  library(data.table),
  library(plot3D),
  library(flextable),
  library(knitr),
  library(kableExtra)
))
```

@@

**Supplementary Table 1. Cluster-specific enriched pathways (effect size >= 0.30).**
```{r enrich-pathway-in-clust, fig.width= 9}
## docx friendly
load("../data/moderate_enrich_prob.Rda")

@@

# st1 <- st1 %>% flextable() %>% 
#   set_caption(caption = "") %>%
#   align(part = "all") %>% 
#   width(., width = c(4,0.75,1,1)) %>% 
#   fontsize(size = 10, part = "body")
# 
# knitr::knit_print(st1)
names(st1) <- c("Pathway", "Cluster", "Effect Size", "-log(p)")
 st1 %>%  knitr::kable(format = "latex", longtable = TRUE, align = c("l", rep("c",3))) %>%
   kable_styling(latex_options=c("scale_down", "repeat_header"), full_width = FALSE, font_size = 12) %>%
   column_spec(1, color = "black", width = "4in")
```
